A Survey on Ordered Binary Decision Diagrams

### 2015-09-10 paper.tex
Fix figure references

Figure~\ref{fig:bdd} shows an example of a BDD representing the Boolean function
$f=(A \land B) \lor (B \land C)$. To simplify the graphs, the diagram style of
Bryant~\cite{BRYANT92} is reused, i.e. edge labels are skipped. Instead dashed
and solid lines are used to represent the value of the decision variable to be 0
and 1, respectively. This diagram style is used throughout this paper.

\begin{figure}[ht]
    \centering
    \subfigure[BDD]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{fig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{fig:obdd}
    }
    \label{fig:bdd-and-obdd}
    \caption{BDD and OBDD of $f=(A \land B) \lor (B \land C)$.}
\end{figure}

@@

Figure~\ref{fig:obdd} shows one possible ROBDD representation of
$f$. The following section covers the details of how
to derive the OBDD representation from a BDD. \tbr

@@

\begin{figure}[ht]
    \centering
    \subfigure[]{
        \includestandalone[height = 3cm]{figs/redundant-nonterminals-before}
        \label{fig:redundant-nonterminals-before}
    }
    \hskip1cm
    \subfigure[]{
        \includestandalone[height = 3cm]{figs/redundant-nonterminals-after}
        \label{fig:redundant-nonterminals-after}
    }
    \label{fig:redundant-nonterminals}
    \caption{Eliminating redundant nonterminal nodes.}
\end{figure}

Figure~\ref{fig:obdd} shows the result of applying the first two transformation
rules to the BDD shown in Figure~\ref{fig:bdd}. The third rule is shown
in Figure~\ref{fig:redundant-nonterminals}.
Figure~\ref{fig:redundant-nonterminals-before} shows a BDD with redundant
nonterminal nodes (both \textbf{B}'s, in essence) and
Figure~\ref{fig:redundant-nonterminals-after} shows the equivalent OBDD without
redundant nonterminals. \tbr

>>>>

Figure~\ref{subfig:bdd} shows an example of a BDD representing the Boolean function
$f=(A \land B) \lor (B \land C)$. To simplify the graphs, the diagram style of
Bryant~\cite{BRYANT92} is reused, i.e. edge labels are skipped. Instead dashed
and solid lines are used to represent the value of the decision variable to be 0
and 1, respectively. This diagram style is used throughout this paper.

\begin{figure}[ht]
    \centering
    \subfigure[BDD]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{subfig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{subfig:obdd}
    }
    \caption{BDD and OBDD of $f=(A \land B) \lor (B \land C)$.}
    \label{fig:bdd-and-obdd}
\end{figure}

@@

Figure~\ref{subfig:obdd} shows one possible ROBDD representation of
$f$. The following section covers the details of how
to derive the OBDD representation from a BDD. \tbr

@@

\begin{figure}[ht]
    \centering
    \subfigure[]{
        \includestandalone[height = 3cm]{figs/redundant-nonterminals-before}
        \label{subfig:redundant-nonterminals-before}
    }
    \hskip1cm
    \subfigure[]{
        \includestandalone[height = 3cm]{figs/redundant-nonterminals-after}
        \label{subfig:redundant-nonterminals-after}
    }
    \caption{Eliminating redundant nonterminal nodes.}
    \label{fig:redundant-nonterminals}
\end{figure}

Figure~\ref{subfig:obdd} shows the result of applying the first two transformation
rules to the BDD shown in Figure~\ref{subfig:bdd}. The third rule is shown
in Figure~\ref{fig:redundant-nonterminals}.
Figure~\ref{subfig:redundant-nonterminals-before} shows a BDD with redundant
nonterminal nodes (both \textbf{B}'s, in essence) and
Figure~\ref{subfig:redundant-nonterminals-after} shows the equivalent OBDD without
redundant nonterminals. \tbr
